### 2022-12-28 sections/experiments/_mitigation_strategies.qmd
camera-ready submitted

```{julia}
n_bootstrap = 10
df = run_bootstrap(results, n_bootstrap; filename=joinpath(output_path,"bootstrap_synthetic.csv"))
```

@@

```{julia}
n_evals = 5
n_rounds = 50
evaluate_every = Int(round(n_rounds/n_evals))
n_folds = 5
T = 100
using Serialization
results = run_experiments(
    experiments;
    save_path=output_path,evaluate_every=evaluate_every,n_rounds=n_rounds, n_folds=n_folds, T=T
)
Serialization.serialize(joinpath(output_path,"results_synthetic_latent.jls"),results)
```

@@

```{julia}
n_bootstrap = 10
df = run_bootstrap(results, n_bootstrap; filename=joinpath(output_path,"bootstrap_latent.csv"))
```

@@

```{julia}
generators = Dict(
    :Generic=>GenericGenerator(decision_threshold=0.5),
    :Latent=>REVISEGenerator(),
    :Generic_conservative=>GenericGenerator(decision_threshold=0.9),
    :Gravitational=>GravitationalGenerator(),
    :ClapROAR=>ClapROARGenerator()
)
```

```{julia}
max_obs = 2500
data_path = data_dir("real_world")
data_sets = load_real_world(max_obs; data_dir=data_path)
choices = [
    :cal_housing, 
    :credit_default, 
    :gmsc, 
]
data_sets = filter(p -> p[1] in choices, data_sets)
```

@@

```{julia}
n_bootstrap = 10
df = run_bootstrap(results, n_bootstrap; filename=joinpath(output_path,"bootstrap_real_world.csv"))
```

@@

```{julia}
using DataFrames, Statistics
model_ = :FluxEnsemble
df = DataFrame() 
for (key, val) in results
    df_ = deepcopy(val.output)
    df_.dataset .= key
    df = vcat(df,df_)
end
df = df[df.n .== maximum(df.n),:]
df = df[df.model .== model_,:]
filter!(:value => x -> !any(f -> f(x), (ismissing, isnothing, isnan)), df)
gdf = groupby(df, [:generator, :dataset, :n, :name, :scope])
df_plot = combine(gdf, :value => (x -> [(mean(x),mean(x)+std(x),mean(x)-std(x))]) => [:mean, :ymax, :ymin])
df_plot = df_plot[[name in [:mmd, :model_performance] for name in df_plot.name],:]
df_plot = df_plot[.!(df_plot.name.==:mmd .&& df_plot.scope.!=:model),:]
df_plot = mapcols(x -> typeof(x) == Vector{Symbol} ? string.(x) : x, df_plot)
transform!(df_plot, :dataset => (X -> [x=="cal_housing" ? "California Housing" : x for x in X]) => :dataset)
transform!(df_plot, :dataset => (X -> [x=="credit_default" ? "Credit Default" : x for x in X]) => :dataset)
transform!(df_plot, :dataset => (X -> [x=="gmsc" ? "GMSC" : x for x in X]) => :dataset)
transform!(df_plot, :name => (X -> [x=="mmd" ? "MMD (model)" : x for x in X]) => :name)
transform!(df_plot, :name => (X -> [x=="model_performance" ? "Performance" : x for x in X]) => :name)
transform!(df_plot, :generator => (X -> [x=="Generic" ? "Generic (γ=0.5)" : x for x in X]) => :generator)
transform!(df_plot, :generator => (X -> [x=="Generic_conservative" ? "Generic (γ=0.9)" : x for x in X]) => :generator)

>>>>

```{julia}
n_bootstrap = 100
df = run_bootstrap(results, n_bootstrap; filename=joinpath(output_path,"bootstrap_synthetic.csv"))
```

@@

```{julia}
n_evals = 5
n_rounds = 50
evaluate_every = Int(round(n_rounds/n_evals))
n_folds = 5
T = 100
using Serialization
results = run_experiments(
    experiments;
    save_path=output_path, evaluate_every=evaluate_every, n_rounds=n_rounds, n_folds=n_folds, T=T, 
    latent_space = true
)
Serialization.serialize(joinpath(output_path,"results_synthetic_latent.jls"),results)
```

@@

```{julia}
n_bootstrap = 100
df = run_bootstrap(results, n_bootstrap; filename=joinpath(output_path,"bootstrap_latent.csv"))
```

@@

```{julia}
max_obs = 2500
data_path = data_dir("real_world")
data_sets = load_real_world(max_obs)
choices = [
    :cal_housing, 
    :credit_default, 
    :gmsc, 
]
data_sets = filter(p -> p[1] in choices, data_sets)
```

@@

```{julia}
n_bootstrap = 100
df = run_bootstrap(results, n_bootstrap; filename=joinpath(output_path,"bootstrap_real_world.csv"))
```

@@

```{julia}
using DataFrames, Statistics
model_ = :FluxModel
df = DataFrame() 
for (key, val) in results
    df_ = deepcopy(val.output)
    df_.dataset .= key
    df = vcat(df,df_)
end
df = df[df.n .== maximum(df.n),:]
df = df[df.model .== model_,:]
filter!(:value => x -> !any(f -> f(x), (ismissing, isnothing, isnan)), df)
gdf = groupby(df, [:generator, :dataset, :n, :name, :scope])
df_plot = combine(gdf, :value => (x -> [(mean(x),mean(x)+std(x),mean(x)-std(x))]) => [:mean, :ymax, :ymin])
df_plot = df_plot[[name in [:mmd, :model_performance] for name in df_plot.name],:]
df_plot = df_plot[.!(df_plot.name.==:mmd .&& df_plot.scope.!=:model),:]
df_plot = mapcols(x -> typeof(x) == Vector{Symbol} ? string.(x) : x, df_plot)
transform!(df_plot, :dataset => (X -> [x=="cal_housing" ? "California Housing" : x for x in X]) => :dataset)
transform!(df_plot, :dataset => (X -> [x=="credit_default" ? "Credit Default" : x for x in X]) => :dataset)
transform!(df_plot, :dataset => (X -> [x=="gmsc" ? "GMSC" : x for x in X]) => :dataset)
transform!(df_plot, :name => (X -> [x=="mmd" ? "MMD (model)" : x for x in X]) => :name)
transform!(df_plot, :name => (X -> [x=="model_performance" ? "Performance" : x for x in X]) => :name)
transform!(df_plot, :generator => (X -> [x=="Generic" ? "Generic (γ=0.5)" : x for x in X]) => :generator)
transform!(df_plot, :generator => (X -> [x=="Generic_conservative" ? "Generic (γ=0.9)" : x for x in X]) => :generator)

### 2022-12-28 sections/experiments/_real_world.qmd
merry xmas
camera-ready submitted

### Real-World Data

@@

```{julia}
models = [
    :LogisticRegression, 
    :FluxModel, 
    :FluxEnsemble
]
generators = Dict(
    :Greedy=>GreedyGenerator(), 
    :Generic=>GenericGenerator(),
    :REVISE=>REVISEGenerator(),
    :DICE=>DiCEGenerator(),
)
```

```{julia}
max_obs = 2500
data_sets = load_real_world(max_obs)
choices = [
    :cal_housing, 
    :credit_default, 
    :gmsc, 
]
data_sets = filter(p -> p[1] in choices, data_sets)
```

@@

#### Bootstrap

```{julia}
n_bootstrap = 10
df = run_bootstrap(results, n_bootstrap; filename=joinpath(output_path,"bootstrap.csv"))
```

#### Chart in paper

>>>>

## Real-World Data

@@

```{julia}
models = [
    :LogisticRegression, 
    :FluxModel, 
    :FluxEnsemble
]
opt = Flux.Descent(0.01) 
generators = Dict(
    :Greedy=>GreedyGenerator(), 
    :Generic=>GenericGenerator(opt = opt),
    :REVISE=>REVISEGenerator(opt = opt),
    :DICE=>DiCEGenerator(opt = opt),
)
```

```{julia}
max_obs = 5000
data_sets = load_real_world(max_obs)
choices = [
    :cal_housing, 
    :credit_default, 
    :gmsc, 
]
data_sets = filter(p -> p[1] in choices, data_sets)
```

@@

### Bootstrap

```{julia}
n_bootstrap = 100
df = run_bootstrap(results, n_bootstrap; filename=joinpath(output_path,"bootstrap.csv"))
```

### Chart in paper

### 2022-12-28 sections/experiments/_synthetic.qmd
camera-ready submitted

```{julia}
n_bootstrap = 10
df = run_bootstrap(results, n_bootstrap; filename=joinpath(output_path,"bootstrap.csv"))
```

@@

```{julia}
# generate_artifacts(output_path)
# generate_artifacts(www_path)
```

>>>>

```{julia}
n_bootstrap = 100
df = run_bootstrap(results, n_bootstrap; filename=joinpath(output_path,"bootstrap.csv"))
```

@@

```{julia}
generate_artifacts(output_path)
generate_artifacts(www_path)
```
